Adaption of the Chumbley Score to matching of bullet striation marks

### 2017-10-11 doc/paper.Rmd
couple of comments

@@

\hh{Some of the test results are missing - we should look into the numbers and parameter settings for those.}

```{r missings, fig.width=8, fig.height=5, fig.cap="Number of failed tests."}
ns <- all %>% group_by(wv, wo, match) %>% summarize(
  n_ss = mean(same_shift_n),
  n_ds = mean(diff_shift_n),
  zero_ss = sum(same_shift_n==0),
  zero_ds = sum(diff_shift_n==0),
  miss = sum(is.na(p_value))
)
ns %>% filter(wv %in% c(30, 50)) %>% 
  ggplot(aes(x = wo, y = miss/85491*100, shape=factor(wv), colour = factor(match))) + 
  geom_smooth(method="lm", size=.5, se=FALSE) +
  geom_point() + 
  theme_bw() +
  ylab("Percent of failed tests.") +
  xlab("Size of optimization window") +
  scale_colour_brewer("Match", palette="Set1") +
  scale_shape_discrete("Size of \nvalidation\nwindow")

>>>>

\hh{'considered to be unique' by AFTE - that is right, but we should not use this argument, and I don't think we have to. It's better to focus on the problem at hand: striation marks are used to determine same source for bullets. XXX we could include some figures here XXX Current standards ask for a visual inspection of the marks under a comparison microscope by a firearms examiner. One of the problems raised by the PCAST report in 2009 is the subjectivity involved in this comparison. There are different approaches used to achieve more objectivity and assess error rates. XXX here we need some examples of approaches XXX
For toolmarks, the Chumbley score has been suggested to determine same-source. XXX summary of results from original paper and the adjustment XXX
In this paper we are interested in how this method has to be adjusted to best be applied to the smaller marks on bullets. }

@@

```{r missings, fig.width=8, fig.height=5, fig.cap="Number of failed tests."}
ns <- all %>% group_by(wv, wo, match) %>% summarize(
  n_ss = mean(same_shift_n),
  n_ds = mean(diff_shift_n),
  zero_ss = sum(same_shift_n==0),
  zero_ds = sum(diff_shift_n==0),
  miss = sum(is.na(p_value)),
  missperc = miss/85491*100
)
ns %>% filter(wv %in% c(30, 50)) %>% 
  ggplot(aes(x = wo, y = missperc, shape=factor(wv), colour = factor(match))) + 
  geom_smooth(method="lm", size=.5, se=FALSE) +
  geom_point() + 
  theme_bw() +
  ylab("Percent of failed tests.") +
  xlab("Size of optimization window") +
  scale_colour_brewer("Match", palette="Set1") +
  scale_shape_discrete("Size of \nvalidation\nwindow")

```
Figure \ref{fig:missings} gives an overview of the number of failed tests, i.e. tests in which a particular parameter setting did not return a valid result. This happens, when the shift to align two signatures is so large, that the remaining overlap is too small to accommodate  windows for validation. The problem is therefore exacerbated by a larger validation window. 
Figure \ref{fig:missings} also shows that the number of failed tests is approximately linear in the size of the optimization window.

```{r lms, results='asis'}
nsnest <- ns %>% filter(wv %in% c(30,50)) %>% group_by(match, wv) %>% nest()
nsnest <- nsnest %>% mutate(
  model = data %>% purrr::map(.f = function(d) lm(I(missperc*100)~wo, data=d)),
  coefs = model %>% purrr::map(.f = broom::tidy)
)
tab <- nsnest %>% unnest(coefs) %>% filter(term=="wo") %>% arrange(match) %>%
  select(-term, -statistic, -p.value)
knitr::kable(tab, digits=3, caption = "Estimates of the increase in percent of failed tests corresponding to a 100 point increase in the optimization window.", booktabs=TRUE)
```
